%-------------------------
% Resume in Latex
% Author : Amlaan Bhoi
% Adapted from: Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex, hidelinks]{hyperref}
\usepackage{fancyhdr}

\usepackage[charter]{mathdesign} % Bitstream Charter
% \usepackage{newpxtext,newpxmath} % Palatino

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.50in}
\addtolength{\evensidemargin}{-0.50in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemNoBullet}[2]{
  \item[]\small{
    \hspace{-9pt}\textbf{#1}{: #2 \vspace{-6pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item[]
  \begin{tabular*}{0.98\textwidth}{l@{\extracolsep{\fill}}r}
      \hspace{-10pt}\textbf{#1} & #2 \\
      \hspace{-10pt}\textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% custom commands
\newcommand{\shorterSection}[1]{\vspace{-10pt}\section{#1}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{center}
  \small \textbf{\href{abhoi.github.io}{\huge Paras Qadir Memon}} \\ 
  Fulbright PhD Student, Colorado State University, Fort Collins, CO \\
  \small 1500 West Plum, 14H, Fort Collins, Colorado, USA \\
  \href{mailto:memon@colostate.edu}{\color{blue}\underline{memon@colostate.edu}} $\vert$ 970-412-5890
\end{center}



%---------------SUMMARY---------------

\shorterSection{Summary}
  \resumeSubHeadingListStart
  \small
    \item{Assistant Professor with three years of teaching experience in academia.}
    \vspace{-5pt}
    \item{Currently, pursuing a doctoral degree in computer science with specialization in brain computer interface.} 
    \vspace{-5pt}
    \item{Possess a significant knowledge of Machine Learning Techniques.} 
    \vspace{-5pt}
    \item{In depth knowledge of Artificial Neural Network libraries, Tensorflow, Scikit-Learn, Numpy, Pandas, Jupyter and Keras.} 
    \vspace{-5pt}
    \item{Technical knowledge of Apache spark, Apache Storm and Hadoop File System using big data.} 
    \vspace{-5pt}
    \item{All round technical knowledge and experience with web development, Object Oriented Programming,
    Python and Fortran.} 
        
    %\vspace{-5pt}
    

\resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\shorterSection{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Colorado State University}{Fort Collins, CO}
      {PhD Student}{Expected August 2022}
    \resumeSubheading
      {UniversityTeknology PETRONAS}{Ipoh, Malaysia}
      {Master of Science Information Technology}{Feb 2015}
    \resumeSubheading
      {Mehran University of Engineering and Technology}{Jamshoro, Pakistan}
      {Bachelor of Software Engineering}{Dec 2011}      
      

  \resumeSubHeadingListEnd




%-----------EXPERIENCE-----------------
\shorterSection{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Department of Computer Science, CSU} {Fort Collins, USA}
      {PhD student}{August 2018 - Present}
      \vspace{2pt}
      \resumeItemListStart
      {Work on Brain Computer Interface (BCI) using Tripolar Concentric Ring Electrode (TCRE)
        Electroencephalogram (EEG).}
      \resumeItemListEnd

    \resumeSubheading
      {Department of Computer Science, IBA University}{Sukkur, Pakistan}
      {Assistant Professor}{April 2018 - Present}
      \vspace{2pt}
      \resumeItemListStart
      {Currently on sabbatical leave to complete PhD degree}
      \resumeItemListEnd
      
    \resumeSubheading
      {Department of Computer Science, IBA University}{Sukkur, Pakistan}
      {Lecturer}{October 2015 - April 2018}
      \resumeItemListStart
      {Teaching and research work in Artificial Intelligence}
      \resumeItemListEnd
      
    \resumeSubheading
      {Department of Computer Information and Sciences, UTP}{Ipoh, Malaysia}
      {Graduate Research Assistant}{January 2013 - February 2015}
      \vspace{2pt}
      \resumeItemListStart
      {Involved in Enhanced Oil Recovery (EOR) project using Artificial Neural Network (ANN) and Data Mining (DM) Techniques.} \\
      Project: "Implementation of Artificial Neural Network for Multiphase Flow Simulation."
      
      \resumeItemListEnd     

  \resumeSubHeadingListEnd





%-----------PROJECTS-----------------
\shorterSection{Projects}
  \resumeSubHeadingListStart
    \item \textbf{Current PhD Title:}
     {Brain computer Interface using Tripolar Concentric Ring Electrode (TCRE) EEG.} \vspace{-5pt}
    \item
    {Predicting Pediatric Bone Age from X-rays Using Convolutional Neural Network.} \vspace{-5pt}
    \item
    {Hyperlink-Induced Topic Search (HITS) over Wikipedia Articles using Apache Spark.} \vspace{-5pt}
    \item
    {Detecting the Most Popular Topics from Live Twitter Message Streams using the Lossy Counting Algorithm with Apache Storm.} 

  \resumeSubHeadingListEnd
  
%-----------Achievements----------------
\shorterSection{Achievements}
  \resumeSubHeadingListStart
    \item
      {PhD Scholarship 2018 - 2022, Fulbright - U.S Department of State}
      \vspace{-5pt}
    \item
      {2010 Global UGRAD Exchange Program in Pakistan, Fulbright Scholarship USA}
       
  
  

%-----------Publications-----------------
\shorterSection{Publication}
  \resumeSubHeadingListStart
  \small
    \item{\textbf{Journal Paper - Paras Q. Memon}, Suet-Peng Yong, William Pao, "Dynamic Modelling of Surrogate Reservoir Model", JURNAL TEKNOLOGI: ADVANCE COMPUTATIONAL INTELLIGENCE WITH BIG DATA, publisher UTM Press, indexed in SCOPUS,.}
    \vspace{0pt}
    \item{\textbf{Paras Q. Memon}, Suet-Peng Yong, William Pao, "Surrogate Reservoir Model for Average Reservoir Pressure", IEEE Technically Sponsored SAI Intelligence System Conference 2016, September/2016, London, UK.}
    \vspace{0pt}
    \item{\textbf{Paras Q. Memon}, Suet-Peng Yong, William Pao, "Dynamic Surrogate Reservoir Model with Well Constraints", The 3rd International Conference on Computer and Information Sciences, Ausgust/2016, Malaysia.}
    \vspace{0pt}
    \item{Book Chapter - Pau J. Sean, William Pao, Suet-­‐‑Peng Yong and Paras Q. Memon, "Evaluation of Relative Permeability Models in CO2/Brine System Using Mixed and Hybrid Finite Element Method," International Meeting on Advances in Thermofluids (IMAT), Kuala Lumpur, 2014.}
    \vspace{0pt}
    \item{\textbf{Book Chapter - Paras Q. Memon}, Suet-­‐‑Peng Yong, William Pao and Pau J. Sean, "Dynamic Well Bottom-Hole Flowing Pressure Prediction based on Radial Basis Neural Network." Springer Book Series-­‐‑ Studies in Computational Intelligence, Indexed by BLP, Ulrichs, SCOPUS, MathSciNet, Current Mathematical Publications, Zentralblatt Math: MetaPress and Springerlink.}
    \vspace{0pt}
    \item{\textbf{Paras Q. Memon}, Suet-Peng Yong, William Pao and Pau J. Sean, "Surrogate Reservoir Modeling - Prediction of Bottom-Hole Flowing Pressure using Radial Basis Neural Network." Science and Information Conference 2014, August/2014, , London, UK.}
    \vspace{0pt}
    \item{Journal Paper - Pau J. Sean, William Pao, Suet-­‐‑Peng Yong and Paras Q. Memon, "Effects of Capillary Pressure on Multiphase Flow During CO2 Injection in Saline Aquifer." The 4th International Conference on Production, Energy and Reliability, June/2014, Malaysia.}
    \vspace{0pt}
    \item{\textbf{Paras Q. Memon}, Suet-Peng Yong, William Pao and Pau J. Sean, "Predicting Bottom Hole Flowing Pressure Using Artificial Neural Network." The 2nd Internal Conference on Computer and Information and Sciences, June/2014, Malaysia}
    \vspace{0pt}
    \item{\textbf{Paras Q. Memon}, Suet-Peng Yong, William Pao and Pau J. Sean, "A Preliminary Study on Well-Based Surrogate Reservoir Model." 2013 IEEE Student Conference on Research & Development (SCOReD), December/2013, Malaysia
}
  \resumeSubHeadingListEnd
%-------------------------------------------





\end{document}